### 2025-09-22 src/articles/article10.qmd
Fix glossary

1. Brothers on Academic Probation are required to make a grade improvement plan with the Scholarship Chair.
   a. The grade improvement plan will be approved by the Scholarship Chair, the President, and the brother. Failure to follow the grade improvement plan as judged by the Scholarship Chair will result in the brother being brought up for standards.
   a. A brother on Academic Probation is allowed to attend at maximum 3 social events per semester. Their responsibilities for rush are reduced to one third (rounded down) of events. This brother will not be allowed to hold an elected position.

@@

   a. Any brother with a cumulative Grade Point Average (GPA) of less than 3.0 or an immediately previous semester GPA of less than 3.0 will be placed on Academic Probation until the end of the semester and will be required to attend an Academic Review as described in Article XII, Section K.
      i. The Academic Review must be within the first two weeks of being put on Academic Probation.

   a. If a brother has a midterm progress GPA of less than 3.0, the Scholarship Chair may request the brother to make a grade improvement plan in accordance with Article X, Section A, Item 2a.

   a. If a brother is participating in a program where they do not receive a GPA (e.g. a Co-op) but would otherwise be placed on Academic Probation:
      i. They are not placed on Academic Probation that semester.
      i. The next semester in which they are not participating in such a program, they will be placed on Academic Probation.

@@

1. During the New Member program, the Scholarship Chair will meet with New Members during a regular New Member meeting to explain the chapter Scholarship Program and answer any questions they have.
1. New Members will be held to the academic standards in Article X, Section A.
1. Candidates will be required to sign the grade releases no later than 14 days of grade releases being made available.
1. A candidate is eligible for initiation if they achieved higher than a 3.0 GPA in the previous semester, or if they have a cumulative GPA of greater than 2.5. Upon receiving a Candidate's GPA, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
   a. First semester freshmen are exempt from this rule.
1. Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.
   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an absolute majority vote by the active chapter.

@@

1. The President, Scholarship Chair, Alumni Advisor, and Faculty Advisor are permitted to know the GPA of each brother.
1. All brothers are permitted to know the names of brothers on Academic Probation. 3. All brothers are permitted to know the names of brothers who cannot hold office due to grades.

>>>>

1. Brothers on {{< var glossary.academic-probation >}} are required to make a {{< var glossary.grade-improvement-plan >}} with the Scholarship Chair.
   a. The {{< var glossary.grade-improvement-plan >}} will be approved by the Scholarship Chair, the President, and the brother. Failure to follow the {{< var glossary.grade-improvement-plan >}} as judged by the Scholarship Chair will result in the brother being brought up for standards.
   a. A brother on {{< var glossary.academic-probation >}} is allowed to {{< var glossary.attend >}} at maximum 3 {{< var glossary.social-event >}}s per semester. Their responsibilities for rush are reduced to one third (rounded down) of events. This brother will not be allowed to hold an elected position.

@@

   a. Any brother with a cumulative Grade Point Average ({{< var acronyms.gpa >}}) of less than 3.0 or an immediately previous semester {{< var acronyms.gpa >}} of less than 3.0 will be placed on {{< var glossary.academic-probation >}} until the end of the semester and will be required to {{< var glossary.attend >}} an Academic Review as described in Article XII, Section K.
      i. The Academic Review must be within the first two weeks of being put on {{< var glossary.academic-probation >}}.

   a. If a brother has a midterm progress {{< var acronyms.gpa >}} of less than 3.0, the Scholarship Chair may request the brother to make a {{< var glossary.grade-improvement-plan >}} in accordance with Article X, Section A, Item 2a.

   a. If a brother is participating in a program where they do not receive a {{< var acronyms.gpa >}} (e.g. a Co-op) but would otherwise be placed on {{< var glossary.academic-probation >}}:
      i. They are not placed on {{< var glossary.academic-probation >}} that semester.
      i. The next semester in which they are not participating in such a program, they will be placed on {{< var glossary.academic-probation >}}.

@@

1. During the New Member program, the Scholarship Chair will meet with New Members during a regular New Member meeting to explain the chapter Scholarship Program and answer any questions they have.
1. New Members will be held to the academic standards in Article X, Section A.
1. Candidates will be required to sign the grade releases no later than 14 days of grade releases being made available.
1. A candidate is eligible for initiation if they achieved higher than a 3.0 {{< var acronyms.gpa >}} in the previous semester, or if they have a cumulative {{< var acronyms.gpa >}} of greater than 2.5. Upon receiving a Candidate's {{< var acronyms.gpa >}}, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
   a. First semester freshmen are exempt from this rule.
1. Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.
   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an {{< var glossary.absolute-majority >}} vote by the active chapter.

@@

1. The President, Scholarship Chair, Alumni Advisor, and Faculty Advisor are permitted to know the {{< var acronyms.gpa >}} of each brother.
1. All brothers are permitted to know the names of brothers on {{< var glossary.academic-probation >}}. 3. All brothers are permitted to know the names of brothers who cannot hold office due to grades.

### 2025-09-22 src/articles/article11.qmd
Fix glossary

1. No brother will reveal the secrets of the fraternity to anyone who is not an initiated member of Theta Chi Fraternity.
1. All brothers will obey all federal, state, and local laws.
1. All brothers will obey all University regulations and the Interfraternity Congress (IFC) Constitution and Bylaws.
1. All brothers will obey the International Bylaws (IBL).
1. All brothers will obey the local bylaws and the provisions of the lease on the fraternity house.

@@

1. Rush
   a. Brothers will attend an amount of Rush events as specified by the Rush Plan.

1. Social
   a. Brothers will attend a majority of social events each semester unless they are on Academic Probation.
   a. Brothers not on Academic Probation will be involved in at least one non-greek campus student organization.

@@

   a. When an event is declared an official chapter event by Executive Council (EC), all members must attend it unless excused by EC. A missed official chapter event that is not excused will count as an unexcused mandatory event.
      i. Missing a mandatory event without an accepted excuse will count as unexcused.
      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.\
      i. A brother who has three unexcused mandatory events throughout the semester will be staggard.
      i. A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.
      i. A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the secretary with the possibility of recommendation for suspension.

   a. Brothers will attend chapter meetings as outlined in Article III, Section C.

1. Committees
   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in Article V, Section G.
   a. Brothers will attend assigned committee meetings as outlined in Article V, Section G.

>>>>

1. No brother will reveal the secrets of the fraternity to anyone who is not an initiated member of Theta Chi Fraternity.
1. All brothers will obey all federal, state, and local laws.
1. All brothers will obey all University regulations and the Interfraternity Congress ({{< var acronyms.ifc >}}) Constitution and Bylaws.
1. All brothers will obey the International Bylaws ({{< var acronyms.ibl >}}).
1. All brothers will obey the local bylaws and the provisions of the lease on the fraternity house.

@@

1. Rush
   a. Brothers will {{< var glossary.attend >}} an amount of Rush events as specified by the Rush Plan.

1. Social
   a. Brothers will {{< var glossary.attend >}} a majority of {{< var glossary.social-event >}}s each semester unless they are on {{< var glossary.academic-probation >}}.
   a. Brothers not on {{< var glossary.academic-probation >}} will be involved in at least one non-greek campus student organization.

@@

   a. When an event is declared an {{< var glossary.official-chapter-event >}} by Executive Council ({{< var acronyms.ec >}}), all members must {{< var glossary.attend >}} it unless excused by {{< var acronyms.ec >}}. A missed {{< var glossary.official-chapter-event >}} that is not excused will count as an unexcused mandatory event.
      i. Missing a mandatory event without an accepted excuse will count as unexcused.
      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.\
      i. A brother who has three unexcused mandatory events throughout the semester will be {{< var glossary.staggard >}}.
      i. A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.
      i. A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the secretary with the possibility of recommendation for suspension.

   a. Brothers will {{< var glossary.attend >}} chapter meetings as outlined in Article III, Section C.

1. Committees
   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in Article V, Section G.
   a. Brothers will {{< var glossary.attend >}} assigned committee meetings as outlined in Article V, Section G.

### 2025-09-22 src/articles/article12.qmd
Fix glossary

1. This section's purpose is to summarize the Standards Board Hearing Procedures in the International Bylaws (IBL), as well as describing the procedure for Academic Review. For more detailed procedures on Standards Board Trials, refer to IBL Article V, Section 22.

@@

1. To judge infractions of the bylaws and standards of the chapter as well as all other laws and rules brothers must adhere to as defined in IBL Article V, Section 22(a).
1. To run Academic Reviews.

@@

1. The composition of Standards Board includes the Vice President as the chair, the Chaplain, and three additional at-large members (IBL Article V, Section 22(b)).
1. The terms of office of the members of Standards Board are outlined in the IBL Article V, Section 22(c). 3. Vacancies should be filled according to IBL Article V, Section 22(g).

@@

1. Unless otherwise specified, votes of the board are by simple majority.
1. Quorum of the board consists of ⅘ of its members.
1. The voting members of the board are the Chaplain and the three at-large members (IBL Article V, Section 22(i)).
1. The Vice President may only vote in the case of a tie (IBL Article V, Section 22(i)).

@@

1. If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council (EC) position, that at-large member is immediately removed from office.
1. Any At-Large Member may be removed for the following reasons:
   a. Failure to perform their duties, including unexcused absence from more than one board meeting per semester.
   a. Failure to maintain confidentiality of all proceedings of the board.\
   a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
   a. At-large members can only be removed by an absolute supermajority vote of the active chapter (IBL Article V, Section 22(e)).

@@

1. Upon receiving the Accusation, the Vice President will decide whether or not a hearing will take place (IBL Article V, Section 22(j)(2)).
   a. The Vice President may request the First Guard and Second Guard to advise him as to whether or not there should be a hearing.
   a. If the Vice President decides that there will not be a hearing, proceedings will end and no hearing will be held.

1. If there is to be a hearing, the Vice President will then decide whether the hearing will be a Standards Board Hearing or a Chapter Hearing.
   a. The Vice President may not request advice from anyone other than a Chapter Advisor on this matter.
   a. If the accuser and/or accused disagree with the decision of which type of hearing the accusations are brought to, they may appeal the decision.
   a. The appeal will be brought exclusively to the voting members of Standards Board to vote on whether the appeal is valid.
      i. If the appeal is found to be valid, the Vice President's decision on the type of hearing will be overruled.

@@

1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
   a. The possible pleas are responsible plea, not responsible plea, and no contest plea.\
   a. If a plea is not received within the twenty-four hours specified above, a no contest plea will be entered.

1. After a plea is entered, the Vice President will schedule a time and place for the hearing.
   a. The hearing shall occur between 1 and 3 weeks after a plea is entered.
   a. The Vice president will notify the accused and accuser of the time, date, and location of the hearing.
      i. If a Standards Board Hearing is to be held, the Vice President will also notify the Chaplain and the at-large members of Standards Board of the time, date, and location of the hearing.
      i. If a Chapter Hearing is to be held, the Vice President will inform all non-suspended brothers of the active chapter and the Chapter Advisory Board (CAB) of the time, date and location of the hearing.

1. The Vice President will inform EC of the accusation, the accused, and the nature of the complaint at the next EC meeting.

1. Recusal
   a. Members of the board will recuse themselves from the hearing if they feel a conflict of interest exists or they are the accused.
   a. Members of the board may be recused by simple majority vote of the remaining board. The accused, accuser, or a member of the board may call for such a vote.
   a. Members of the Standards Board may recuse themselves. Members of Standards Board, the accused, or accuser may call for a vote to recuse any member of Standards Boardup to the beginning of the trial.
   a. Vacancies due to recusal should be filled in accordance with IBL Article V, Section 22(j)(9)(v) or (vi), as they apply to the situation.

@@

1. The accused may then be asked questions by the members of Standards Board and the Chapter Advisor (if he is present) with a time limit as voted on by the voting members of Standards Board.

@@

1. Witnesses that wish to speak for the charges will be chosen in an order decided by the Vice President to give a statement. The accused, Chapter Advisor (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.

1. Witnesses that wish to speak against the charges will be chosen in an order decided by the Vice President to give a statement. The accused, Chapter Advisor (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.

@@

1. The voting members of Standards Board will determine if the accused is responsible or not responsible for the accusations brought forth against him.
   a. The Vice President and Chapter Advisor (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
   a. Any member of Standards Board may recall any witnesses or the accused, if further questions arise. This may be done once per witness. To recall a witness more than once requires a unanimous vote of the voting members of Standards Board.

1. The voting members of Standards Board will then determine appropriate sanctions, if any.
   a. Past judicial history of the accused and sanctions given for similar accusations in the past (as found in Appendix B) may be considered.
   a. The Vice President and Chapter Advisor (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
   a. The voting members of Standards Board will vote on all sanctions, one at a time.
   a. If the sanction being voted on is temporary suspension for any duration of time, the vote must be unanimous in the affirmative in order to succeed.

@@

1. The accused may appeal a decision of Standards Board.
   a. Appeals must be submitted within 7 days after receiving written notification of the results of the hearing.
   a. If an appeal is made, the confidentiality of the hearing is waived starting at the next regularly scheduled chapter meeting at which quorum is present.

@@

1. Appeals will be presented to the active chapter at the next regularly scheduled chapter meeting at which quorum is present.

@@

1. If the decision is overturned, the chapter may give new sanctions by simple majority vote.

@@

1. A quorum of Standards Board is required to hold an Academic Review.

@@

1. A member of Standards Board may be recused from an Academic Review under the following circumstances:
   a. Members of the board for whom the Scholarship Chair is requesting a suspension trial will recuse themselves.
   a. Members of Standards Board will recuse themselves if they feel a conflict of interest exists.
   a. Members of Standards Board may be recused by a simple majority vote of the remaining members of Standards Board. The brother under review, the Scholarship Chair, or a member of Standards Board may call for such a vote.

@@

   b. Preparation:
      i. The brother under review is not required to attend.
      i. Both the brother under review and the Scholarship Chair may provide witnesses and any form of relevant documents, including written statements. If either the brother under review or the Scholarship Chair cannot attend the review, any such documents must be sent to the Vice President along with an order of any witnesses to be called.
      i. The Vice President will call the meeting to order and ask all but unrecused members of the board, the Scholarship Chair, and the brother under review to leave the room.

>>>>

1. This section's purpose is to summarize the Standards Board Hearing Procedures in the International Bylaws ({{< var acronyms.ibl >}}), as well as describing the procedure for Academic Review. For more detailed procedures on Standards Board Trials, refer to {{< var acronyms.ibl >}} Article V, Section 22.

@@

1. To judge infractions of the bylaws and standards of the chapter as well as all other laws and rules brothers must adhere to as defined in {{< var acronyms.ibl >}} Article V, Section 22(a).
1. To run Academic Reviews.

@@

1. The composition of Standards Board includes the Vice President as the chair, the Chaplain, and three additional at-large members ({{< var acronyms.ibl >}} Article V, Section 22(b)).
1. The terms of office of the members of Standards Board are outlined in the {{< var acronyms.ibl >}} Article V, Section 22(c). 3. Vacancies should be filled according to {{< var acronyms.ibl >}} Article V, Section 22(g).

@@

1. Unless otherwise specified, votes of the board are by {{< var glossary.simple-majority >}}.
1. {{< var glossary.quorum >}} of the board consists of ⅘ of its members.
1. The voting members of the board are the Chaplain and the three at-large members ({{< var acronyms.ibl >}} Article V, Section 22(i)).
1. The Vice President may only vote in the case of a tie ({{< var acronyms.ibl >}} Article V, Section 22(i)).

@@

1. If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council ({{< var acronyms.ec >}}) position, that at-large member is immediately removed from office.
1. Any At-Large Member may be removed for the following reasons:
   a. Failure to perform their duties, including unexcused absence from more than one board meeting per semester.
   a. Failure to maintain confidentiality of all proceedings of the board.\
   a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
   a. At-large members can only be removed by an {{< var glossary.absolute-supermajority >}} vote of the active chapter ({{< var acronyms.ibl >}} Article V, Section 22(e)).

@@

1. Upon receiving the Accusation, the Vice President will decide whether or not a hearing will take place ({{< var acronyms.ibl >}} Article V, Section 22(j)(2)).
   a. The Vice President may request the First Guard and Second Guard to advise him as to whether or not there should be a hearing.
   a. If the Vice President decides that there will not be a hearing, proceedings will end and no hearing will be held.

1. If there is to be a hearing, the Vice President will then decide whether the hearing will be a Standards Board Hearing or a Chapter Hearing.
   a. The Vice President may not request advice from anyone other than a {{< var glossary.chapter-advisor >}} on this matter.
   a. If the accuser and/or accused disagree with the decision of which type of hearing the accusations are brought to, they may appeal the decision.
   a. The appeal will be brought exclusively to the voting members of Standards Board to vote on whether the appeal is valid.
      i. If the appeal is found to be valid, the Vice President's decision on the type of hearing will be overruled.

@@

1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
   a. The possible pleas are {{< var glossary.responsible-plea >}}, {{< var glossary.not-responsible-plea >}}, and {{< var glossary.no-contest-plea >}}.\
   a. If a plea is not received within the twenty-four hours specified above, a {{< var glossary.no-contest-plea >}} will be entered.

1. After a plea is entered, the Vice President will schedule a time and place for the hearing.
   a. The hearing shall occur between 1 and 3 weeks after a plea is entered.
   a. The Vice president will notify the accused and accuser of the time, date, and location of the hearing.
      i. If a Standards Board Hearing is to be held, the Vice President will also notify the Chaplain and the at-large members of Standards Board of the time, date, and location of the hearing.
      i. If a Chapter Hearing is to be held, the Vice President will inform all non-suspended brothers of the active chapter and the Chapter Advisory Board ({{< var acronyms.cab >}}) of the time, date and location of the hearing.

1. The Vice President will inform {{< var acronyms.ec >}} of the accusation, the accused, and the nature of the complaint at the next {{< var acronyms.ec >}} meeting.

1. Recusal
   a. Members of the board will recuse themselves from the hearing if they feel a conflict of interest exists or they are the accused.
   a. Members of the board may be recused by {{< var glossary.simple-majority >}} vote of the remaining board. The accused, accuser, or a member of the board may call for such a vote.
   a. Members of the Standards Board may recuse themselves. Members of Standards Board, the accused, or accuser may call for a vote to recuse any member of Standards Boardup to the beginning of the trial.
   a. Vacancies due to recusal should be filled in accordance with {{< var acronyms.ibl >}} Article V, Section 22(j)(9)(v) or (vi), as they apply to the situation.

@@

1. The accused may then be asked questions by the members of Standards Board and the {{< var glossary.chapter-advisor >}} (if he is present) with a time limit as voted on by the voting members of Standards Board.

@@

1. Witnesses that wish to speak for the charges will be chosen in an order decided by the Vice President to give a statement. The accused, {{< var glossary.chapter-advisor >}} (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.

1. Witnesses that wish to speak against the charges will be chosen in an order decided by the Vice President to give a statement. The accused, {{< var glossary.chapter-advisor >}} (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.

@@

1. The voting members of Standards Board will determine if the accused is {{< var glossary.responsible >}} or {{< var glossary.not-responsible >}} for the accusations brought forth against him.
   a. The Vice President and {{< var glossary.chapter-advisor >}} (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
   a. Any member of Standards Board may recall any witnesses or the accused, if further questions arise. This may be done once per witness. To recall a witness more than once requires a unanimous vote of the voting members of Standards Board.

1. The voting members of Standards Board will then determine appropriate sanctions, if any.
   a. Past judicial history of the accused and sanctions given for similar accusations in the past (as found in Appendix B) may be considered.
   a. The Vice President and {{< var glossary.chapter-advisor >}} (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
   a. The voting members of Standards Board will vote on all sanctions, one at a time.
   a. If the sanction being voted on is temporary suspension for any duration of time, the vote must be unanimous in the affirmative in order to succeed.

@@

1. The accused may appeal a decision of Standards Board.
   a. Appeals must be submitted within 7 days after receiving written notification of the results of the hearing.
   a. If an appeal is made, the confidentiality of the hearing is waived starting at the next regularly scheduled chapter meeting at which {{< var glossary.quorum >}} is present.

@@

1. Appeals will be presented to the active chapter at the next regularly scheduled chapter meeting at which {{< var glossary.quorum >}} is present.

@@

1. If the decision is overturned, the chapter may give new sanctions by {{< var glossary.simple-majority >}} vote.

@@

1. A {{< var glossary.quorum >}} of Standards Board is required to hold an Academic Review.

@@

1. A member of Standards Board may be recused from an Academic Review under the following circumstances:
   a. Members of the board for whom the Scholarship Chair is requesting a suspension trial will recuse themselves.
   a. Members of Standards Board will recuse themselves if they feel a conflict of interest exists.
   a. Members of Standards Board may be recused by a {{< var glossary.simple-majority >}} vote of the remaining members of Standards Board. The brother under review, the Scholarship Chair, or a member of Standards Board may call for such a vote.

@@

   b. Preparation:
      i. The brother under review is not required to {{< var glossary.attend >}}.
      i. Both the brother under review and the Scholarship Chair may provide witnesses and any form of relevant documents, including written statements. If either the brother under review or the Scholarship Chair cannot {{< var glossary.attend >}} the review, any such documents must be sent to the Vice President along with an order of any witnesses to be called.
      i. The Vice President will call the meeting to order and ask all but unrecused members of the board, the Scholarship Chair, and the brother under review to leave the room.

### 2025-09-22 src/articles/article13.qmd
Fix glossary

1. The Vice President of the chapter presides over the hearing as Arbiter. If the Vice President is unable to serve or not present, the Chaplain will preside over the hearing as Arbiter.
1. If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing. If this is not possible, the highest position on Executive Council (EC) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.

@@

1. Unless otherwise specified, votes during a Chapter Hearing are by simple majority. 2. Every member of the chapter who is present for the hearing is a voting member. 3. The Arbiter will only vote in the case of a tie.
   a. Quorum of the hearing consists of ⅔ of the chapter.

@@

1. The chapter will then determine whether the accused is responsible or not responsible.

1. The chapter will then determine appropriate sanctions, if any.
   a. Past judicial history of the accused and sanctions given for similar accusations in the past may be considered.
   a. There will be a discussion to determine each specific sanction. After discussion comes to a close, the sanctions decided upon must be passed by a supermajority of present members vote. If the vote is not passed, the chapter will return to discussion.

@@

1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:\
   a. Counseling
   a. Loss of housing status
   a. Loss of voting privileges
   a. Recommendation of Removal from an Elected Position
   a. Recommendation of Suspension
   a. Probation

>>>>

1. The Vice President of the chapter presides over the hearing as Arbiter. If the Vice President is unable to serve or not present, the Chaplain will preside over the hearing as Arbiter.
1. If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing. If this is not possible, the highest position on Executive Council ({{< var acronyms.ec >}}) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.

@@

1. Unless otherwise specified, votes during a Chapter Hearing are by {{< var glossary.simple-majority >}}. 2. Every member of the chapter who is present for the hearing is a voting member. 3. The Arbiter will only vote in the case of a tie.
   a. {{< var glossary.quorum >}} of the hearing consists of ⅔ of the chapter.

@@

1. The chapter will then determine whether the accused is {{< var glossary.responsible >}} or {{< var glossary.not-responsible >}}.

1. The chapter will then determine appropriate sanctions, if any.
   a. Past judicial history of the accused and sanctions given for similar accusations in the past may be considered.
   a. There will be a discussion to determine each specific sanction. After discussion comes to a close, the sanctions decided upon must be passed by a {{< var glossary.supermajority >}} of present members vote. If the vote is not passed, the chapter will return to discussion.

@@

1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:\
   a. Counseling
   a. Loss of housing status
   a. Loss of voting privileges
   a. Recommendation of Removal from an Elected Position
   a. Recommendation of Suspension
   a. {{< var glossary.probation >}}

### 2025-09-22 src/articles/article14.qmd
Fix glossary

1. This section's purpose is to summarize the Suspension and Expulsion Procedures in the International Bylaws (IBL). For more detailed procedures, refer to IBL Article VI, Section 13.

@@

1. To determine whether suspension or expulsion is warranted due to violations of their obligation to the Fraternity. These violations include:
   a. Conduct that indicates he is unworthy to represent, bear the name of, or wear the badge of the Fraternity.
   a. A violation of any oaths taken during Ritual.
   a. A violation of the limitations on memberships as detailed in IBL Article VI, Section 12.
   a. Participation in an initiation conducted in violation of IBL Article VI, Section 4(e).
   a. A violation of any financial obligation to the active chapter.

@@

1. After the meeting is called to order and a quorum is determined to be present, the president shall read the accusations, withholding the name of the accuser. The meeting may proceed whether or not the accused member attends.
1. Witnesses (members or non-members) may be called by any member, including the accused, to testify as to their knowledge of the accusations. Members, including the accused, may ask questions of any witness.
1. The accused has the right to speak on their own behalf. Members may ask questions of the accused.
1. After all witnesses have been heard, the accused shall withdraw from the meeting. Members then ballot upon the motion to suspend and/or expel the accused. The affirmative vote of a simple majority of all collegiate members eligible to vote shall be necessary to sustain a motion to suspend. A ¾ vote of all collegiate members eligible to vote shall be necessary to expel, except for cases in which the accused member is confirmed to have led or participated in hazing, in which case only a simple majority vote of all collegiate members of the active chapter eligible to vote is needed to expel the member.
1. If two or more members have been accused of the same or related conduct and the hearings of the accusations for such members have been scheduled for a single meeting, all accused members shall withdraw from the meeting before members vote on any of the options. No such accused member shall be eligible to vote with respect to a motion relating to any other of the accused.
1. The result of the votes on all resolutions shall be promptly communicated to the accused member, who shall govern themselves accordingly.
1. No record of the proceeding with respect to an accused member shall be retained unless the motion to suspend or expel is sustained.
   a. If the motion to expel is sustained, the chapter shall promptly send International Headquarters (IHQ) a copy of the notice of meeting served; a complete statement of the original accusations and any written response made by the accused; a numerical record of the number of all members eligible to vote, the number of members eligible and present for the vote, and the number of such members voting for the motion; a summary of all evidence submitted by all witnesses; a copy of the minutes of the meeting recording the action of the chapter.
   a. If a motion to suspend is sustained, the chapter shall promptly report the suspension to IHQ.

@@

1. If the chapter deems that lifting a suspension given by this section is appropriate, the president of the active chapter which imposed the suspension shall receive a petition signed by more than ⅓ of all collegiate members of the chapter seeking to lift the suspension.
1. The president shall call and conduct a meeting in accordance with IBL Article VI, Section 13(b), paragraphs 1 through 7, excluding paragraph 4, and including the first sentence of paragraph 8.
1. The members shall ballot upon a motion to lift the suspension. This motion needs the affirmative vote of at least ½ of all collegiate members of the chapter eligible to vote in order to sustain the motion.

>>>>

1. This section's purpose is to summarize the Suspension and Expulsion Procedures in the International Bylaws ({{< var acronyms.ibl >}}). For more detailed procedures, refer to {{< var acronyms.ibl >}} Article VI, Section 13.

@@

1. To determine whether suspension or expulsion is warranted due to violations of their obligation to the Fraternity. These violations include:
   a. Conduct that indicates he is unworthy to represent, bear the name of, or wear the badge of the Fraternity.
   a. A violation of any oaths taken during Ritual.
   a. A violation of the limitations on memberships as detailed in {{< var acronyms.ibl >}} Article VI, Section 12.
   a. Participation in an initiation conducted in violation of {{< var acronyms.ibl >}} Article VI, Section 4(e).
   a. A violation of any financial obligation to the active chapter.

@@

1. After the meeting is called to order and a {{< var glossary.quorum >}} is determined to be present, the president shall read the accusations, withholding the name of the accuser. The meeting may proceed whether or not the accused member {{< var glossary.attend >}}s.
1. Witnesses (members or non-members) may be called by any member, including the accused, to testify as to their knowledge of the accusations. Members, including the accused, may ask questions of any witness.
1. The accused has the right to speak on their own behalf. Members may ask questions of the accused.
1. After all witnesses have been heard, the accused shall withdraw from the meeting. Members then {{< var glossary.ballot >}} upon the motion to suspend and/or expel the accused. The affirmative vote of a {{< var glossary.simple-majority >}} of all collegiate members eligible to vote shall be necessary to sustain a motion to suspend. A ¾ vote of all collegiate members eligible to vote shall be necessary to expel, except for cases in which the accused member is confirmed to have led or participated in hazing, in which case only a {{< var glossary.simple-majority >}} vote of all collegiate members of the active chapter eligible to vote is needed to expel the member.
1. If two or more members have been accused of the same or related conduct and the hearings of the accusations for such members have been scheduled for a single meeting, all accused members shall withdraw from the meeting before members vote on any of the options. No such accused member shall be eligible to vote with respect to a motion relating to any other of the accused.
1. The result of the votes on all resolutions shall be promptly communicated to the accused member, who shall govern themselves accordingly.
1. No record of the proceeding with respect to an accused member shall be retained unless the motion to suspend or expel is sustained.
   a. If the motion to expel is sustained, the chapter shall promptly send International Headquarters ({{< var acronyms.ihq >}}) a copy of the notice of meeting served; a complete statement of the original accusations and any written response made by the accused; a numerical record of the number of all members eligible to vote, the number of members eligible and present for the vote, and the number of such members voting for the motion; a summary of all evidence submitted by all witnesses; a copy of the minutes of the meeting recording the action of the chapter.
   a. If a motion to suspend is sustained, the chapter shall promptly report the suspension to {{< var acronyms.ihq >}}.

@@

1. If the chapter deems that lifting a suspension given by this section is appropriate, the president of the active chapter which imposed the suspension shall receive a petition signed by more than ⅓ of all collegiate members of the chapter seeking to lift the suspension.
1. The president shall call and conduct a meeting in accordance with {{< var acronyms.ibl >}} Article VI, Section 13(b), paragraphs 1 through 7, excluding paragraph 4, and including the first sentence of paragraph 8.
1. The members shall {{< var glossary.ballot >}} upon a motion to lift the suspension. This motion needs the affirmative vote of at least ½ of all collegiate members of the chapter eligible to vote in order to sustain the motion.

### 2025-09-22 src/articles/article2.qmd
Fix glossary

1. The legislation of this chapter will be superseded by the Theta Chi International Bylaws (IBL), Theta Chi International Legislation, legislation passed by the Grand Chapter of Theta Chi Fraternity, and the Beta Nu of Theta Chi Local Bylaws.

@@

1. Temporary Legislation:
   a. Must be passed by a simple majority vote.
   a. Expires one year from the date of passage unless a date of expiration is specified.

1. Permanent Legislation:
   a. Must be passed by a simple majority vote.
   a. Remains in effect indefinitely, until revoked or amended as specified below.

1. Emergency Legislation:
   a. Can be passed by a simple majority of those present (even if quorum is not present).
   a. At the next chapter meeting where quorum is present, the Vice President will bring the emergency legislation before the chapter as permanent or temporary legislation.

1. Executive Edicts:
   a. Must be approved by an absolute majority vote of Executive Council (EC), which immediately puts the edict into effect as legislation.
      i. At the next chapter meeting at which quorum is present, the Vice President will bring the edict before the chapter as permanent or temporary legislation. The chapter must then approve the legislation for the edict to remain in effect.
   a. Supersedes all previous legislation.

@@

1. The legislation of this chapter may be revoked or amended by a simple majority vote.
1. No legislation can be revoked or amended if quorum is not present with the exception of Emergency Legislation.

>>>>

1. The legislation of this chapter will be superseded by the Theta Chi International Bylaws ({{< var acronyms.ibl >}}), Theta Chi International Legislation, legislation passed by the Grand Chapter of Theta Chi Fraternity, and the Beta Nu of Theta Chi Local Bylaws.

@@

1. Temporary Legislation:
   a. Must be passed by a {{< var glossary.simple-majority >}} vote.
   a. Expires one year from the date of passage unless a date of expiration is specified.

1. Permanent Legislation:
   a. Must be passed by a {{< var glossary.simple-majority >}} vote.
   a. Remains in effect indefinitely, until revoked or amended as specified below.

1. Emergency Legislation:
   a. Can be passed by a {{< var glossary.simple-majority >}} of those present (even if {{< var glossary.quorum >}} is not present).
   a. At the next chapter meeting where {{< var glossary.quorum >}} is present, the Vice President will bring the emergency legislation before the chapter as permanent or temporary legislation.

1. Executive Edicts:
   a. Must be approved by an {{< var glossary.absolute-majority >}} vote of Executive Council ({{< var acronyms.ec >}}), which immediately puts the edict into effect as legislation.
      i. At the next chapter meeting at which {{< var glossary.quorum >}} is present, the Vice President will bring the edict before the chapter as permanent or temporary legislation. The chapter must then approve the legislation for the edict to remain in effect.
   a. Supersedes all previous legislation.

@@

1. The legislation of this chapter may be revoked or amended by a {{< var glossary.simple-majority >}} vote.
1. No legislation can be revoked or amended if {{< var glossary.quorum >}} is not present with the exception of Emergency Legislation.
